Appendix

### 2019-09-26 manuscript/appendix/appendix.Rmd
wip

# r <- uniform(0, 1)
# Q <- uniform(0, 10)
#K <- uniform(0, 10)
a <- uniform(0, 10)
# H <- uniform(0,  2)
#sigma <- uniform(0, 1)

@@

```{r}
a <- unname(sample(unlist(draws, TRUE), 100))
p$N <- 1e3
x <- sim_data %>% filter(reps == lows[[1]], t == 2001) %>% pull(x)

@@

```{r}

posterior_sims %>% 
  mutate(a = as.numeric(a), 
         t = t+2000) %>% 
  ggplot(aes(t,x)) + 
  geom_line(aes(group = reps), col = "blue", alpha = 0.05,
            data = true_forecast) + 
  geom_line(aes(group = a), alpha = 0.05, col = "red") + 
  geom_line(data = training_set) 
```

>>>>

r <- uniform(0, 2 * p$r)
Q <- uniform(0, 10)
K <- uniform(0, 2*p$K)
a <- uniform(0, 10)
H <- uniform(0,  2*p$H)
sigma <- uniform(0, 2 * p$sigma)

@@

```{r}
#a <- unname(sample(unlist(draws, TRUE), 100))
x0 <- sim_data %>% filter(reps == lows[[1]], t == 2001) %>% pull(x)

posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(100)

posterior_samples %>%
  mutate(N=1e3, x0 = x0) %>%
  purrr::transpose() %>% map_dfr()

p$N <- 1e3

@@
